---
title: "Quarto and targets example"
format: html
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr} 
  %\VignetteIndexEntry{Quarto and targets example}
  %\usepackage[UTF-8]{inputenc}
---

<!--
https://r-pkgs.org/vignettes.html#sec-vignettes-workflow-writing

generate the contents of a sample quarto .qmd file that includes an example of a targets pipeline
-->

# Introduction

This is a quarto document that uses the targets package to create a reproducible pipeline. The pipeline consists of the following steps:

- Download some data from the web using `tar_target()`.
- Clean the data and filter out some rows using `tar_target()`.
- Plot the data using `tar_target()`.
- Render this document using `tar_render()`.

# Setup

We load the required packages and set some options.

```{r setup, include = FALSE}
# library(quarto)
library(wordparse)
library(targets)
# library(tarchetypes)
# library(tidyverse) # 
library(ggplot2)

options(tidyverse.quiet = TRUE)

# https://stackoverflow.com/questions/30237310/setting-work-directory-in-knitr-using-opts-chunksetroot-dir-doesnt-wor
# change of the working directory affects not the current but only the next chunk. So e. g. if you want to load data relative to the new working directory do that in the following chunk.
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = FALSE
                      , comment = NA
                      , warning = FALSE
                      , error = FALSE
                      , message = FALSE
                      , tidy = TRUE)
```


# Pipeline
We define the pipeline using a 
list of target objects. 
We use the 
`tar_target()` function to 
create regular targets, and the 
`tar_render()` function to 
create a special target that renders this document.

## step 1 - load and process data
+ We use the mtcars dataset from R 
+ create a new variable called mpg01 that indicates whether the miles per gallon is above or below the median.

```{r functions.R}
# FIXME: this creates functions.R-1.png
# in ~/Documents_GitHub/wordparse/vignettes/targets_pipeline_em_files/figure-html
# i.e. plott creates a png of the plot?!
print(getwd())
# TODO: ../R v ./R ?
source("../R/plan_vig_targets.R") # Some custom functions for the pipeline
tar_make() # essential else dataa doesnt exist?!
tar_read(dataa)

```

```{r tar_script}
# creates vignette/_targets.R
# puts library(targets) as first line
tar_script(tar_target(xx, 1 + 1), ask = FALSE)
tar_make()
tar_read(xx)
```

## second step - fit a linear model 
+ of mpg01 as a function of wt and hp
+ use the glm function with a binomial family.

```{r step_2}
tar_read(modell)
```

## third step - plot predicted probabilities 
+ of mpg01 as a function of wt and hp
+ use the predict function to get the probabilities and the ggplot2 package to create the plot.
```{r step_3}
tar_read(plott)
```

## run the pipeline
+ use `targets::tar_make()` function
+ execute the targets in order and skip any targets that are already up to date
+ output objects stored in a hidden folder called _targets/objects/.
```{r tar_make}
# to create _targets folder
targets::tar_make()
```

To display the output of a target, we use the tar_read() function. For example, here is the summary of the model:
```{r modell}
tar_read(modell) |> summary()
```

And here is the plot:
```{r read_plott}
tar_read(xx)
tar_read(plott)
```


```
  # Render document
  tar_render(
    report,
    "report.qmd"
  )
```

# Output
We can use the 
`tar_load()` and 
`tar_read()` 
functions to access the output of the targets in the pipeline. For example, we can load the plot target and display it in the document.

```{r load plott}
tar_load(plott)
```

We can also use the `targets::tar_visnetwork()` function to visualize the dependency graph of the pipeline.

```{r tar_visnetwork}
targets::tar_visnetwork()
```

# Conclusion
This document shows how to use the targets package with quarto to create a reproducible pipeline. The document itself is part of the pipeline, and it will be re-rendered whenever any of its dependencies change. This ensures that the output is always up to date and consistent with the code.

